Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-11-08 draft.tex
clean up main text of prop 1 proof

Recall that either outside actor could invest toward increasing any of the six state variables in a period: $q_{st},q_{gt},w_{st},w_{gt},l_{st},$ and $l_{gt}$. However, each outside actor only considers investments in three of the state variables as treated in the three cases in Definition 2. The remainder of the proof treats each set of matched investment decisions in turn.

@@

Consider period 1. When Restriction (4) holds, the patron will want to invest just enough to create a buffer of $\frac{\beta}{1-\de}$ between $Q_{s1} \ (= q_{s1} + R_{s1})$ and $l_{s1}$ so that $c$ will not invest. That is, in equilibrium, $R_{p1} = \frac{\beta}{1-\de} -(q_{s1} - l_{s1})$ as long as $p$ can afford to make this investment. Thus we need Restriction (5): $B_{p1} \geq\frac{\beta}{1-\de} - \left(q_{s1} - l_{s1} \right)$, where $B_{p1}$ is the amount $p$ has available to spend on the conflict in period $1$.

@@

With the equilibrium status quo investments determined, we can proceed to Lemma 3, which rules out spending for or against recognition of the secessionist state:

\begin{lemma}
When Restriction 4 holds, the international community's willingness to invest to avoid recognition of the secessionist state is sufficient to deter the patron from investing to achieve recognition.
\end{lemma}

@@

\begin{lemma}
Restrictions 3 and 4 ensure that the international community's willingness to invest to discourage new conflict is sufficient to deter the patron from investing to instigate such fighting.
\end{lemma}

>>>>

Recall that either outside actor could invest toward increasing any of the six state variables in a period: $q_{st},q_{gt},w_{st},w_{gt},l_{st},$ and $l_{gt}$. However, each outside actor only considers investments in three of the state variables as treated in the three cases in Definition 2. The remainder of the proof addresses each set of matched investment decisions in turn.

@@

Consider period 1. When Restriction (3) holds, the patron will want to invest just enough to create a buffer of $\frac{\beta}{1-\de}$ between $Q_{s1} \ (= q_{s1} + R_{s1})$ and $l_{s1}$ so that $c$ will not invest. That is, in equilibrium, $R_{p1} = \frac{\beta}{1-\de} -(q_{s1} - l_{s1})$ as long as $p$ can afford to make this investment. Thus we need Restriction (5): $B_{p1} \geq\frac{\beta}{1-\de} - \left(Q_{s0} - \mu - L_{s0} \right)$, where $B_{p1}$ is the amount $p$ has available to spend on the conflict in period $1$.

@@

With the equilibrium status quo investments determined, we can proceed to Lemma 3, which rules out spending by the patron to help achieve recognition of the secessionist state:

\begin{lemma}
When Restriction (4) of Definition 1 holds, the international community's willingness to invest to avoid recognition of the secessionist state is sufficient to deter the patron from investing to achieve recognition.
\end{lemma}

@@

\begin{lemma}
Restrictions (3) and (4) of Definition 1 ensure that the international community's willingness to invest to discourage new conflict is sufficient to deter the patron from investing to instigate such fighting.
\end{lemma}
